The R programming for Bayesian Statics Course
========================================================

## Question 1
### Draw by Var
## 
$$
\hat{\delta}^{\pi}(x)=\frac{\sum^{m}_{i=1}\theta_{i}exp\{-||x-\theta_{i}||^{2}/2\}}{\sum^{m}_{i=1}exp\{-||x-\theta_{i}||^{2}/2\}}
$$

```{r}

ts<-function(miu){
mean=rep(0,1000)
for (i in 1:1000){
  mean[i]<-sit(x=miu)
}
var(mean)
}
sit<-function(x=4){
rcauchy(10,location=0,scale=1)->rr
sum=0
div=0
for (i in 1:10){
  sum=rr[i]*exp(-(x-rr[i])^2/2)+sum
  div=exp(-(x-rr[i])^2/2)+div
}
sum/div
}
set.seed(763428)
miu=seq(0,6,by=0.1)
var=rep(0,61)
for (i in 1:61){
  var[i]<-ts(miu[i])
}
plot(miu,var)
```


## Question 1.2
### Draw by Scatter

```{r}
ts<-function(miu){
mean=rep(0,1000)
for (i in 1:1000){
  mean[i]<-sit(x=miu)
}
mean
}
sit<-function(x=4){
rcauchy(10,location=0,scale=1)->rr
sum=0
div=0
for (i in 1:10){
  sum=rr[i]*exp(-(x-rr[i])^2/2)+sum
  div=exp(-(x-rr[i])^2/2)+div
}
sum/div
}
set.seed(93521)
miu=seq(0,6,by=0.1)
mean<-ts(miu[1])
mu<-rep(0,1000)
for (i in 2:61){
  mean<-c(mean,ts(miu[i])-miu[i])
  mu<-c(mu,rep(miu[i],1000))
}
library(ggplot2)
g<-ggplot(,aes(mu,mean))
g+geom_point()
```


## Question 2 simulate for OLS and LAE
### LAE is computed by quantreg packages
### It shows that there are not as many diffierences as we thought
## Equation: $Y=1+0.5x+\epsilon$
```{r,results="hide"}
library(quantreg)
b1=rep(0,1000)
b2<-b1
b3<-b2
b4<-b3
for (i in 1:1000){
x<-runif(100,-100,100)
e1<-rnorm(100)
e2<-rt(100,3)
y=1+x*0.5+e1
y1=1+x*0.5+e2
fit1<-lm(y~x)
fit1$coefficients[2]->b1[i]
fit2<-rq(y~x,0.5)
fit2$coefficients[2]->b2[i]
fit3<-lm(y1~x)
fit3$coefficients[2]->b3[i]
fit4<-rq(y1~x,0.5)
fit4$coefficients[2]->b4[i]
}
```
### OLS method $\epsilon \thicksim N(0,1)$
```{r}
summary(b1)
```
### LAE method $\epsilon \thicksim N(0,1)$
```{r}
summary(b2)
```
### OLS method $\epsilon \thicksim t(3)$
```{r}
summary(b3)
```
### LAE method $\epsilon \thicksim t(3)$
```{r}
summary(b4)
```

## Question 3 MCMC
### simulate the mean of normal distribution N(3,5)
```{r,fig.width=13,fig.height=10}
library(ggplot2)
mcmc_test<-function(x0=0,n1=1000,bw=1,label=NULL){
  p<-runif(n1)
  w<-rnorm(n1)
  x[1]<-x0
  for (i in 2:n1){
    y<-x[i-1]+w[i]*bw
    r<-min(dnorm(y,3,5)/dnorm(x[i-1],3,5),1)
    if (r>p[i]){
      x[i]<-y
    }else{
      x[i]<-x[i-1]
    }
  }
  data.frame(n=1:n1,x=x,label=rep(label,n1))->data
}
data1<-mcmc_test(100,bw=5,label="x0=100,n=1000,bw=5")
data2<-mcmc_test(100,bw=1,label="x0=100,n=1000,bw=1")
data3<-mcmc_test(10,bw=5,label="x0=10,n=1000,bw=5")
data4<-mcmc_test(100,n=10000,bw=1,label="x0=10,n=10000,bw=5")
rbind(data1,data2,data3,data4)->data
pic<-ggplot(data,aes(n,x),col=label)
pic+geom_path(aes(colour=label))+
  facet_wrap(~label,ncol=2,scales="free_x")
```
